% LaTeX version of the departmental syllabus required for Spring 2013 and later,
% originally sent by Dr. Tam on Jan 1, 2013.

% Change the following variables and compile the document to create a PDF
% syllabus.
% Make sure syllabus_input.tex is in the same folder.

%%%%%%%%%%%%%%%%%%
% Mandatory Data %
%%%%%%%%%%%%%%%%%%

% Here's all the mandatory information you must provide
% (per departmental policy):

% Title stuff
  % Course Code, ex: MATH 1000-080
\newcommand{\CourseCode}{
MATH 3142-001
}
  % Course Name
\newcommand{\CourseName}{
Advanced Calculus of Several Variables
}
  % Semester
\newcommand{\Semester}{
Spring 2016
}

% Instructor data
  % Your name
\newcommand{\InstName}{
Dr. Steven Clontz
}
  % Your office number
\newcommand{\OffLoc}{
Fretwell 380G
}
  % Your office hours
\newcommand{\OffHours}{
TR 1300-1500
}
  % Your office phone number
\newcommand{\OffPhone}{
(704) 687-0620
}
  % Your email address
\newcommand{\Email}{
sclontz5@uncc.edu
}

% Course data
  % Classroom location
\newcommand{\ClassLoc}{
Fretwell 306
}
  % Lecture times (line 1)
\newcommand{\ClassTimeOne}{
TR 1230-1345
}
%   % Lecture times (line 2)
% \newcommand{\ClassTimeTwo}{
% }
  % Final exam time (line 1)
\newcommand{\FinalExamOne}{
Thu 2016/05/12 1100-1330
}
%   % Final exam time (line 2)
% \newcommand{\FinalExamTwo}{
% }
  % Number of credit hours
\newcommand{\CreditHrs}{
3
}
  % Textbook to be used
\newcommand{\Text}{
Advanced Calculus (Fitzpatrick)
}


% Course Description
\newcommand{\CourseDesc}{
Multivariable analysis, including (but not limited to) some subset
of the following topics:
Continuity and differentiability of functions of several variables,
inverse and implicit function theorems, integration, Fubini's theorem,
change of variables, the classical integral theorems of Gauss, Green and
Stokes and their generalizations.
}

\newcommand{\mc}{\mathcal}
% Grade Description
\newcommand{\GradeDesc}{
During the semester, you will be assesed based on note checks \(N\),
presentations \(P\), and a midterm \(M\),
and your semester grade is calculated as
\(S=\frac{N+P+M}{3}\).

A final exam \(X\) will be administered, and
your overall grade reported to the university is calculated as
\(G=\max(\{\frac{2S+X}{3},\frac{S+2X}{3}\})\).


\begin{tabular}{|c|c|}\hline
\textbf{Letter Grade} & \textbf{Percentage}\\\hline\hline
A & 90\% - 100\%\\
B & 80\% - 89\%\\
C & 70\% - 79\%\\
D & 65\% - 69\%\\
F & 0\% - 64\%\\\hline
\end{tabular}
}

% % Grade Distribution
%   % Table partitioning credit for each assignment
% \newcommand{\GradeDist}{
% \begin{tabular}{|l|l|}\hline
% Test 1 & \(250\) \\
% Test 2 & \(250\) \\
% Test 3 & \(250\) \\
% Final Exam & \(250^\star\) \\\hline\hline
% Total & 1000\\\hline
% \end{tabular}
% }

% % Letter Grade Assignment
%   % Table partitioning assignment of letter grades by percentage and points
% \newcommand{\LetterAssign}{
% \begin{tabular}{|c|c|c|}\hline
% \bf{Grade} & \bf{Points} & \bf{Percentage}\\\hline\hline
% A & 900-1000 & 90\% - 100\%\\
% B & 800-899 & 80\% - 89\%\\
% C & 700-799 & 70\% - 79\%\\
% D & 650-699 & 65\% - 69\%\\
% F & 0-649 & 0\% - 64\%\\\hline
% \end{tabular}
% }

% Makeup Policy
\newcommand{\MakeUp}{
If the midterm is missed for an excused reason, it will be replaced with the
grade on the final. If the final is missed for an excused reason, a makeup
will be scheduled as early as possible. Arrangements should be make with the
professor if the note check or presentation grades are affected for an excused
reason. As a rule, only written documentation from a medical professional will
be accepted as an excuse without at least two weeks' advance notice.
}

% Disability/Accomodations Policy
\newcommand{\Accomodations}{
UNC Charlotte is committed to access to education.
Students in this course seeking accommodations for disabilities must
first consult with the Office of Disability Services and follow the
instructions of that office to obtain accommodations.
}

% Academic Honesty
\newcommand{\AcaHon}{
All portions of University Policy 407,
The Code of Student Academic Integrity\\
\centerline{\url{http://legal.uncc.edu/policies/up-407}}\\
will apply to this class. All academic honesty violations
will be reported to the Dean of Students Office.
\textbf{Photo ID may be required at examinations.}
}

% Contingency Plan
  % The default message allows you to change this syllabus as needed
  % (for example, giving one less exam due to time constraints),
  % but you should present the changed policy in writing to your class.
\newcommand{\ContPlan}{
If normal class is disrupted due to unanticipated
circumstances, the syllabus and other course plans and assignments may be
modified. If this occurs, an addendum to your
syllabus and/or course assignments will be provided by the instructor.
}


%%%%%%%%%%%%%%%%%%%%%
% Optional Sections %
%%%%%%%%%%%%%%%%%%%%%

% Extra Sections
  % You can optionally add as many extra sections as you wish by editing the
  % \ExtraSections variable.
  % Set the variable as empty to remove these sections.
\newcommand{\ExtraSections}{
\textbf{Class structure:} \\
This is an upper level mathematics course. As such, it's important for all
students to be engaged in the writing and presentation of the material.
As such, lectures by the professor will be augmented with many student
presentations. Bringing a laptop to lecture is recommended
as notes must be typeset in \LaTeX{} for submission.

\textbf{Presentations:} \\
The professor will provide an outline of the defintions, theorems, and problems
(called a ``theorem sequence'')
which will be updated throughout the course. Students are expected to read ahead
in the textbook on these. The professor will lecture on some topics himself,
and assign some topics as homework (to be included in each students' notes),
but other topics will be presented by students in the class. Depending
on the topic (usually asking for the proof of a theorem), the professor may
ask for a volunteer, choose a specific student, or call on a student randomly.

When called, the student may choose to not present if they are not prepared
(or absent) at most twice during the semester without being assigned a
\(0\) for the presentation. Otherwise, a grade
from the set \(\{100,70,20\}\) is assigned for each presentation.
The professor may drop some individual
presentation grades for students who present more often.
Each students' overall presentation grade is an average of all individual
presentation grades earned.

\textbf{Note checks:} \\
The theorem sequence will be provided with its \LaTeX{} source. Students must
create a free account on Overleaf.com to typeset their own solutions and
proofs to the problems and theorems covered in the sequence, and provide
the professor with a link to this Overleaf project.

The professor will regularly announce
note checks. A grade will be assigned at the professor's discretion based
upon factors such as overall completion or correctness of specific
proofs/solutions.
The professor may or may not inform the class which proofs or solutions will
be graded before the note check occurs.
Each students' overall note check grade is an average of all individual
note check grades earned.

IMPORTANT: plagarism is a violation
of academic honesty and will be reported; do NOT blindly copy solutions, e.g.
from the book, online, another student.
You are allowed (actually, encouraged) to work
with your colleagues on these problems, but all typed notes and solutions
must be your original writing.

\textbf{Midterm and Final:} \\
The midterm and final are both in the same format, except that the final
exam is longer. These exams are comprehensive over material covered up
to that point in class. A short multiple choice portion will be given first,
primarily testing knowledge about definitions and theorems. Following this, an
open-note and open-book portion will be given which asks for solutions/proofs
to several problems/theorems not assigned as part of the theorem sequence.

\textbf{Attendance:} \\
Attendance will not be formally taken every day, but is necessary due to
required presentations.

If you need to miss
class for a reasonable conflict (athletics, etc.) you are encouraged to
have the absence excused by providing documentation to
the professor at least two weeks in advance.
If you miss class due to illness, you should check with the professor
on your first day back to clear any possible missed presentations.
If any other assessments are missed due to illness, you
must email the professor as soon as possible and provide written
documentation from a medical professional within one week of the assessment
for it to be considered excused.

\textbf{Office Hours:} \\
Students are encouraged to meet with the professor during office hours
for help on assigned homework and other feedback on class material.
Office hours are not available the day of an exam.

\textbf{Calculators:} \\
Calculators are not necessary and not allowed on any exam.

\textbf{Moodle:}\\
Many materials materials will be posted online to Moodle.
}

% PostScript
  % You can optionally add a final comment at the end of the syllabus to
  % drive home an important point.
  % Set \PostScript as empty to remove this final comment.
\newcommand{\PostScript}{
% \textbf{ELECTRONIC DEVICES ARE NOT ALLOWED IN CLASS UNLESS GIVEN EXPLICIT
% PERMISSION BY THE INSTRUCTOR.}

% How to update this document: Full instructions are available at \\
% \url{https://github.com/StevenClontz/syllabus} \\
% (Scroll down to view README.md)
}



\input{./includes/body.tex}

